% CV ----
% This is just here so I know exactly what I'm looking at in Rstudio when messing with stuff.
\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=0.5in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
% \usepackage{titlesec}
% \titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}
% \titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\scriptsize  Ariel Mundo Ortiz - Resume}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Ariel Mundo Ortiz:  Resume (Curriculum Vitae)},
            pdfauthor={Ariel Mundo Ortiz},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

% \emph{Updated:} \apstylekinda\today
% ^ removed from that front bar.

\usepackage{orcidlink}
%\usepackage{academicons}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
% \newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}

\begin{document}


\centerline{\huge \bf Ariel Mundo Ortiz}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Postdoctoral Fellow}
\moveleft.5\hoffset\centerline{Centre de Recherche du CHUM}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:aimundo.ortiz@gmail.com}{\nolinkurl{aimundo.ortiz@gmail.com}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +1
438 875
9203  \hspace{1 mm}       \faGlobe \hspace{1 mm} \href{http://aimundo.rbind.io}{\tt aimundo.rbind.io}    | \emph{Updated:} \apstylekinda\today}



\vspace{2 mm}

\hrule



\section{Education}\label{education}

\emph{University of Arkansas}, PhD. Biomedical Engineering \hfill May
2022

\emph{Universidad Rafael Landivar (Guatemala)}, B.S. Chemical
Engineering (\emph{cum laude}) \hfill 2009

\section{Research Experience}\label{research-experience}

\emph{Postdoctoral Fellow, Centre de Recherche du CHUM} (Montreal, QC)
\hfill January 2024- Present

Working at the NG lab at CRCHUM in projects at the intersection of
bioinformatics, vital signs, and personalized medicine. In charge of
developing data analysis pipelines, statistical analyses, manuscript
writing and revision. Postdoctoral research published in \emph{Practical
Laboratory Medicine} and \emph{The Journals of Gerontology: Series A}.

\emph{Postdoctoral Fellow, Département de médecine sociale et préventive
et au centre de recherche en santé publique} (Université de Montréal,
Montreal, QC) \hfill July 2022- December 2023

Worked at the Nasri Lab at the School of Public Health (ESPUM) doing
research in infectious disease modelling, incluiding spatial analyses.
Duties included writing, editing, and revising academic manuscripts,
doing literature searches, collaborating with different research groups,
contributing to ongoing grant projects from the lab, writing code to
clean and analyze data. First year of postdoctoral fellowship was
supported by a CRM-MfPH fellowship. Postdoctoral research published in
\emph{Vaccine} and \emph{One Health}.

\emph{Graduate Research Assistant} (University of Arkansas,
Fayetteville, AR) \hfill Aug 2017- May 2022

Developed research questions to study tumor response to chemoterapy.
Collected data, wrote code for statistical analyses. Writing duties
included as well a grant proposal in collaboration with the main
supervisor. Manuscripts of PhD research were published in
\emph{Statistics in Medicine}, \emph{Neoplasia}, and \emph{Journal of
Biomedical Optics}.

\section{Other Relevant Experience}\label{other-relevant-experience}

\textbf{Universidad Rafael Landivar}

\emph{Teaching Assistant Professor} \hfill 2016-2017

\begin{itemize}
\tightlist
\item
  Professor of Chemistry at the Environmental and Agricultural Sciences
  Department. Duties included developoing lectures, laboratory
  supervision, student mentoring, updating laboratory manuals to reduce
  expenses and minimize ecological impact, and communicating with
  faculty.
\end{itemize}

\emph{Adjunct Professor} \hfill 2013-2017

\begin{itemize}
\tightlist
\item
  Taught Introductory Chemistry in the Engineering, Environmental and
  Agricultural, and Health Sciences Departments. Duties included
  developoing lectures, laboratory supervision, student mentoring,
  updating laboratory manuals to reduce expenses and minimize ecological
  impact, and communicating with faculty.
\end{itemize}

\textbf{Lacteos Balcanicos Glad}

\emph{Assistant Plant Engineer} \hfill 2012

\begin{itemize}
\tightlist
\item
  In charge of the production of the main product (yogurt, \(\approx\)
  3000 L per week). Duties included personnel supervision, material
  inventory, production scheduling, quality control reporting.
\end{itemize}

\section{Publications}\label{publications}

\subsection{Journal Articles}\label{journal-articles}

\textbf{Mundo Ortiz, Ariel I.}, Emond Jean-Philippe, Cheung Vincent
Weng-Jy, Saeed Sahar, Desmarais Philippe, Larivière François, Hétu
Pierre-Olivier \& Nguyen Quoc Dinh. ``The impact of pathological
fluctuations versus biological variation on the interpretation of
laboratory values''. \emph{Practical Laboratory Medicine} (November
2025). \url{https://doi.org/10.1016/j.plabm.2025.e00511}.

Cheung Vincent Weng-Jy, Libotte Michaël, Nguyen Patrick Viet-Quoc, Minh
Vu Thien-Tuong, Émond Jean-Philippe, \textbf{Mundo Ortiz Ariel I.},
Desmarais Philippe,Nguyen Quoc Dinh. ``Preliminary feasibility and
development of a heart rate-based mobility and activity scale for
hospitalized older adults''. \emph{The Journals of Gerontology: Series
A} (November 2025) \url{https://doi.org/10.1093/gerona/glaf212}

El-Mousawi Fatima, \textbf{Mundo Ortiz Ariel I.}, Berkat Rawda, Nasri
Bouchra. ``The Impact of Flood Adaptation Measures on Affected
Population's Mental Health: A mixed method Scoping Review''.
\emph{Disaster Medicine and Public Health Preparedness} (2024).
\url{https://doi.org/10.1101/2023.04.27.23289166}

\textbf{Mundo Ortiz Ariel I.}, Nasri Bouchra. ``Socio-demographic
determinants of COVID-19 vaccine uptake in Ontario: Exploring
differences across the Health Region model''. Vaccine (2024).
\url{https://doi.org/10.1016/j.vaccine.2024.02.045}.

Molla Jeta, Sekkak Idriss, \textbf{Mundo Ortiz Ariel I.}, Moyles Iain,
Nasri Bouchra. ``Mathematical modeling of mpox: a scoping review''. One
Health (2023). \url{https://doi.org/10.1016/j.onehlt.2023.100540}

\textbf{Mundo Ortiz Ariel I.}, Muhammad Abdussaboor, Balza Kerlin,
Nelson Christopher E., Muldoon Timothy J. ``Longitudinal examination of
perfusion and angiogenesis markers in primary colorectal tumors shows
distinct signatures for metronomic and maximum-tolerated dose
strategies''. Neoplasia (2022).
\url{https://doi.org/10.1016/j.neo.2022.100825}

\textbf{Mundo Ortiz Ariel I.}, Tipton John R., Muldoon Timothy J.
``Generalized additive models to analyze non-linear trend sin biomedical
longitudinal data using R: Beyond repeated measures ANOVA and Linear
Mixed Models.'' Statistics in Medicine (2022).
\url{https://doi.org/10.1002/sim.9505}

\textbf{Mundo Ortiz Ariel I.}, Greening Gage, Fahr Michael J., Hale
Lawrence N., Bullard Elizabeth, Rajaram Narasimhan, and Muldoon Timothy
J. ``Diffuse reflectance spectroscopy to monitor murine colorectal tumor
progression and therapeutic response.'' Journal of Biomedical Optics
(2020). \url{https://doi.org/10.1117/1.JBO.25.3.035002}

Greening Gage, \textbf{Mundo Ortiz Ariel I.}, Rajaram Narasimhan,
Muldoon Timothy J. ``Sampling depth of a diffuse re-flectance
spectroscopy probe forin-vivophysiological quantification of murine
subcutaneous tumor allografts''.Journal of Biomedical Optics (2018).
\url{https://doi.org/10.1117/1.JBO.23.8.085006}

\subsection{Conference Presentations}\label{conference-presentations}

\textbf{Mundo Ortiz, Ariel I.} ``Reproducible papers in the life
sciences using R''. CANSSI Statistical Software Conference. November
2022. Recording: \url{https://www.youtube.com/watch?v=4yRAR9fS3pg}

\textbf{Mundo Ortiz, Ariel I.}. ``Statistics and Reproducibility in
Biomedical Research''. 2022 Toronto Workshop on Reproducibility.
Toronto, ON. February 2022. Recording:
\url{https://www.youtube.com/watch?v=Fvkp20X5xwA}

\textbf{Mundo Ortiz, Ariel I.}, Muldoon, Timothy J. ``Longitudinal
optical and molecular quantification provides insight into the effect of
different dosing strategies in colorectal cancer''. 2022 Biophotonics
Congress: Biomedical Optics, Fort Lauderdale, FL, USA, April 2022.

\textbf{Mundo Ortiz, Ariel I.} ``Statistics and Reproducibility in
Biomedical Research: Why we need both''. Toronto Workshop on
Reproducibility, University of Toronto, February 2022. Recording
available \href{https://www.youtube.com/watch?v=Fvkp20X5xwA}{here}.

\textbf{Mundo Ortiz, Ariel I.} ``Using generalized additive models for
biomedical longitudinal data. \emph{When linear models don't work}''.
RMedicine 2021 Conference. Recording: \url{https://tinyurl.com/39epnrp6}
Repository (slides and data):
\url{https://aimundo.rbind.io/talks/gams-biomedical/}

\textbf{Mundo Ortiz, Ariel I.}, Abdussaboor Muhammad, and Timothy J.
Muldoon. ``Optical and molecular longitudinal tracking of primary
colorectal murine tumors shows differences in the angiogenic response to
maximum-tolerated and metronomic approaches.'' In Label-free Biomedical
Imaging and Sensing (LBIS) 2021, vol.~11655, p.~116551C.
\emph{International Society for Optics and Photonics}, 2021.
\url{https://doi.org/10.1117/12.2576906}

\textbf{Mundo Ortiz, Ariel I.}, Elizabeth Bullard, Kyle P. Quinn, and
Timothy J. Muldoon. ``Optical spectroscopic and imaging biomarkers of
ulcerative colitis disease progression and remission (Conference
Presentation).'' In Multiscale Imaging and Spectroscopy, vol.~11216,
p.~1121605. \emph{International Society for Optics and Photonics}, 2020.
\url{https://doi.org/10.1117/12.2543369}

\textbf{Mundo Ortiz, Ariel I.}, Gage J. Greening, and Timothy Muldoon.
``Characterization of a multimodal endoscopically deployable veterinary
spectroscopy and imaging probe to determine therapeutic response in a
murine orthotopic tumor model.'' In Label-free Biomedical Imaging and
Sensing (LBIS) 2019, vol.~10890, p.~108901L. \emph{International Society
for Optics and Photonics}, 2019.

\section{Awards and Recognition}\label{awards-and-recognition}

\emph{Fields Institute: Mathematics for Public Health Festival
(MfPHFest)} \hfill October 2022

Received funding to attend the MfPHFest conference and present
postdoctoral work done in the field of Statistics. (CAD 1,500)

\emph{Centre de recherches mathématiques (CRM) MfPH-CRM Postdoctoral
Fellowship} \hfill July 2022

Received postdoctoral fellowship for one year to analyze public health
and behavioral data (CAD 50,000)

\emph{BME Rising Scholar} \hfill June 2022

Selected by the committee of the BME Scholars Program at Washington
University in St.~Louis to receive mentorship about pathways and
professional success in academic careers. Award included paid travel,
conference attendance and honorarium.

\emph{Professional Awareness, Advancement, and Development (PADD)
Scholar} \hfill 2020-2021

Received funding and participated in the PAAD program to supplement my
graduate education in persuasive speaking, commercialization, and data
science (USD 1,500).

\emph{OMNI Endowed International Scholarship} \hfill 2020

Granted as a scholar fulfilling the mission of the OMNI Center in
Fayetteville (USD 500)

\emph{Fulbright Faculty Development Scholarship} \hfill 2017-2019

Scholarship covered all costs of my PhD for the first two years. Only
two scholarships awarded for that period in the whole country. (USD
78,000)

\section{Grants}\label{grants}

\emph{Canada Institutes of Health Research (CIHR)} \hfill 2023

Co-investigator in the grant ``epidemiological modelling of behavioural
impact on mpox mitigation strategies'' lead by Prof.~Nasri from
Université de Montréal. Involved in the writing of the grant proposal,
performing literature review, communicating with team members, and
revising the final grant draft. Funding secured: CAD 412,000. The
proposal was in the 50\% rank within the competition. Record of the
grant can be found in the
\href{https://webapps.cihr-irsc.gc.ca/decisions/p/project_details.html?applId=481271&lang=en}{CIHR funding decision database}.

\emph{Arkansas Biosciences Institute 2021 seed grant competition }
\hfill 2021

Main author on a proposal co-submitted with Dr.~Timothy Muldoon to
examine gene expression and optically derived markers in a mouse model
of colorectal cancer. Funding secured: USD 30,000. The proposal scored
in the top 2 of all the individual research projects for the cycle.

\section{Languages}\label{languages}

\begin{itemize}
\item
  Spanish: Native speaker
\item
  English: Full professional competency
\item
  French: Full professional competency
\end{itemize}

\end{document}
